Good Empirics Dominate Bad Theory: Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-04 paper.Rmd
update Table 4 replication

\clearpage

![](figures/bands-table4.png)

```{r, message=FALSE}
tab4 <- read_csv("data/tab4-fixed.csv")

tab4 %>%
  knitr::kable(
    caption = "2016 Confusion Matrices for Six-month Escalation Model.",
    booktabs = TRUE
  ) %>%
  kableExtra::collapse_rows(1)
```

>>>>

```{r, message=FALSE}
tab4o <- read_csv("data/table4-original.csv")
tab4f <- read_csv("data/table4-fixed.csv")

tab4o <- tab4o %>%
  rename(header = type) %>%
  mutate(source = "Original, scored with civil war incidence")
tab4f <- tab4f %>%
  rename(Predicted0 = `0`, Predicted1 = `1`) %>%
  mutate(source = "Fixed, scored with civil war onset")

tab4 <- bind_rows(tab4o, tab4f) %>%
  select(source, header, everything())

tab4 %>%
  knitr::kable(
    caption = "Replication of B\\&S Table 4: 2016 Confusion Matrices for Six-month Escalation Model.",
    booktabs = TRUE
  ) %>%
  kableExtra::collapse_rows(1:2, row_group_label_position = "stack")
```
